Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-15 docs/google-research-awards-latam/main.tex
pass on results
merge

    Contact at Google:~Martin Barbella (mbarbella@google.com) and Vilas Jagannath (vilasshekharbj@gmail.com)

@@

\vspace{-2ex}
\begin{abstract}
JavaScript (JS) is a fundamental programming language for the
web. Finding bugs in JavaScript engines is an important
problem. Differential testing of JS engines is a promising approach to
that end. This proposal describes our testing infrastructure, current
results, and some upcoming features to improve the bug-finding
process.
\end{abstract}

@@

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}. 
  The \CodeIn{valueOf} is an object property that returns the primitive value
  of the specific object\cite{valueof} and in the original version of this code,
  the \CodeIn{valueOf} function returns an empty string.
  The modified code returns a string representation of an embedded null terminator
  value. 
  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{Object.ToNumber(a.valueOf())} 
  that converts a variable to a number, otherwise the return should be the 
  value NaN (Not a Number) \cite{unary-plus}.
  As such, the engines evaluate that unary plus as a NaN value 
  at the assertion expression; hence test execution is expected to fail. 
  Chakra, however, is able to parse the string as a number zero, making the test to pass.

>>>>

    Contacts:~Martin Barbella (mbarbella@google.com), Vilas Jagannath (vilasshekharbj@gmail.com)

@@

\vspace{-2ex}
\begin{abstract}
JavaScript (JS) is a fundamental programming language for the
web. Finding bugs in JavaScript engines is an important problem. This
proposal describes our differential testing infrastructure for testing
JS engines, our current results, and upcoming features to improve
bug-finding of JS engines.
\end{abstract}

@@

The workflow described in Section~\ref{sec:design} is currently functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}. 
  The \CodeIn{valueOf} is an object property that returns the primitive value
  of the specific object\cite{valueof} and in the original version of this code,
  the \CodeIn{valueOf} function returns an empty string.
  The modified code returns a string representation of an embedded null terminator
  value. 
  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{Object.ToNumber(a.valueOf())} 
  that converts a variable to a number, otherwise the return should be the 
  value NaN (Not a Number) \cite{unary-plus}.
  As such, the engines evaluate that unary plus as a NaN value 
  at the assertion expression; hence test execution is expected to fail. 
  Chakra, however, is able to parse the string as a number zero, making the test to pass.
